---
title: "An Analysis of Monkeypox Demographics"
description: |
  This project will explore some new data about the current monkeypox outbreak.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

```{r gender-plot}
plot_1 <- read_rds("plot-1.rds")

plot_1 |>
  ggplot(mapping = aes(x = Gender, y = gender_percent, fill = Gender)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_minimal() +
  labs(title = "Percentage of Total Confirmed Monkeypox Cases by Gender", subtitle = "The majority of recorded cases thus far have been in men", x = "Gender", y = "Percent of Total Cases", caption = "Data source: Global.health (2022)") +
  theme(legend.position = "none")
```
At first glance, the current outbreak of monkeypox would appear to be disproportionately affecting men, with over 95% of confirmed cases being recorded in such people. The dataset is from global.health, compiling individual case data originally from a number of governmental institutions worldwide. The data was then cleaned up and plotted in a straightforward manner. While it may appear that monkeypox only impacts gay and bisexual men, this conclusion doesn't complement past outbreaks, and is possibly due to deficits in testing.
